---
title: 'Creating a coefficient table'
author:
- name: Jared Fowler
output:
  html_document: 
    number_sections: no
vignette: >
  %\VignetteIndexEntry{prettyglm: Beautiful Visualisations for Generalized Linear Models}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The function `pretty_coefficients()` allows you to create a pretty table of model coefficients. The table created will automatically include categorical variable base levels, and highlight insignificant p-values.

## Pre-processing

A critical step for this package to work is to **set all categorical predictors as factors**. 

```{r preprocessing 1, echo=TRUE, message=FALSE, warning=FALSE}
library(dplyr)
library(prettyglm)
data('titanic')

# Easy way to convert multiple columns to a factor.
columns_to_factor <- c('Pclass',
                       'Sex',
                       'Cabin', 
                       'Embarked',
                       'Cabintype')
meanage <- base::mean(titanic$Age, na.rm=T)
titanic  <- titanic  %>%
  dplyr::mutate_at(columns_to_factor, list(~factor(.))) %>%
  dplyr::mutate(Age =base::ifelse(is.na(Age)==T,meanage,Age)) 

# Build a basic glm
survival_model <- stats::glm(Survived ~ Pclass + 
                                        Sex + 
                                        Fare +
                                        Age +
                                        Embarked + 
                                        SibSp + 
                                        Parch, 
                             data = titanic, 
                             family = binomial(link = 'logit'))
```

## Table of model coefficients {.tabset}

### Simple Example

The simplest way to call this function is just with the model object.

```{r visualise coefficients, echo=TRUE, message=FALSE, warning=FALSE}
pretty_coefficients(model_object = survival_model)
```

### Type III Significance Tests

You can also complete a type III test on the coefficients by specifying a `type_iii` argument. Warning `Wald` type III tests will fail if there are aliased coefficients in the model.

You can change the significance level highlighted in the table with `significance_level`.

```{r visualise coefficients type iii, echo=TRUE}
pretty_coefficients(survival_model, 
                    type_iii = 'Wald', 
                    significance_level = 0.1)
```

### Changing Variable Importance Method

By default `pretty_coefficients` shows "model" variable importance. But `vimethod` also accepts "permute" and "firm" methods from \link[vip]{vi}. Additional parameters for these methods should also be passed into `pretty_coefficients()`.

```{r visualise coefficients vi, echo=TRUE}
pretty_coefficients(model_object = survival_model,
                    type_iii = 'Wald', 
                    significance_level = 0.1, 
                    vimethod = 'permute', 
                    target = 'Survived', 
                    metric = 'auc',
                    pred_wrapper = predict.glm, 
                    reference_class = 0)
```
