---
title: 'Creating relativity plots for interactions'
author:
- name: Jared Fowler
output:
  html_document: 
    number_sections: no
vignette: >
  %\VignetteIndexEntry{prettyglm: Beautiful Visualisations for Generalized Linear Models}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The function `pretty_relativities()` creates a plot to show the fit of the desired predictor. This vignette shows how to create plots for interacted variables.

## Pre-processing

A critical step for this package to work is to **set all categorical predictors as factors**. 

```{r preprocessing 1, echo=TRUE, message=FALSE, warning=FALSE}
library(dplyr)
library(prettyglm)
data('titanic')

# Easy way to convert multiple columns to a factor.
columns_to_factor <- c('Pclass',
                       'Sex',
                       'Cabin', 
                       'Embarked',
                       'Cabintype')
meanage <- base::mean(titanic$Age, na.rm=T)
titanic  <- titanic  %>%
  dplyr::mutate_at(columns_to_factor, list(~factor(.))) %>%
  dplyr::mutate(Age =base::ifelse(is.na(Age)==T,meanage,Age)) 

# Build a basic glm
survival_model2 <- stats::glm(Survived ~ Pclass:Fare +
                                         Age +
                                         Embarked:Sex +
                                         SibSp +
                                         Parch,
                              data = titanic,
                              family = binomial(link = 'logit'))
```

## Plot interacted coefficients 

A model relativity is a transform of the model estimate. By default `pretty_relativities()` uses 'exp(estimate)-1' which is useful for GLM's which use a log or logit link function. 

`prettyglm` currently only supports interactions of two variables.


### Factor:Factor Interactions {.tabset}

#### Standard

You can create these relativity plots as you would for a non-interaction.

```{r visualise ff N, echo=TRUE, message=FALSE, warning=FALSE}
pretty_relativities(feature_to_plot= 'Embarked:Sex',
                    model_object = survival_model2,
                    relativity_label = 'Liklihood of Survival'
                    )
```

#### Facet

You can also choose to facet the plots by one of the variables.

```{r visualise ff F, echo=TRUE, message=FALSE, warning=FALSE}
pretty_relativities(feature_to_plot= 'Embarked:Sex',
                    model_object = survival_model2,
                    relativity_label = 'Liklihood of Survival',
                    iteractionplottype = 'facet',
                    facetorcolourby = 'Sex'
                    )
```

#### Colour

You can also choose to colour the plots by one of the variables.

```{r visualise ff C, echo=TRUE, message=FALSE, warning=FALSE}
pretty_relativities(feature_to_plot= 'Embarked:Sex',
                    model_object = survival_model2,
                    relativity_label = 'Liklihood of Survival',
                    iteractionplottype = 'colour',
                    facetorcolourby = 'Embarked'
                    )
```



### Continuous:Factor Interactions {.tabset}

#### Colour

By default continuous and factor interaction plots will colour by the factor variable.

```{r visualise cf C, echo=TRUE, message=FALSE, warning=FALSE}
pretty_relativities(feature_to_plot= 'Pclass:Fare',
                    model_object = survival_model2,
                    relativity_label = 'Liklihood of Survival',
                    upper_percentile_to_cut = 0.03
                    )
```

#### Facet

You can also facet by the factor variable. ERROR HERRER

```{r visualise cf F, echo=TRUE, message=FALSE, warning=FALSE}
pretty_relativities(feature_to_plot= 'Pclass:Fare',
                    model_object = survival_model2,
                    relativity_label = 'Liklihood of Survival',
                    iteractionplottype = 'facet',
                    upper_percentile_to_cut = 0.03,
                    height = 800
                    )
```

