---
title: 'Creating simple relativity plots'
author:
- name: Jared Fowler
output:
  html_document: 
    number_sections: no
vignette: >
  %\VignetteIndexEntry{prettyglm: Beautiful Visualisations for Generalized Linear Models}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The function `pretty_relativities()` creates a plot to show the fit of the desired predictor. A different plot will be generated depending on the class of the variable.

## Pre-processing

A critical step for this package to work is to **set all categorical predictors as factors**. 

```{r preprocessing 1, echo=TRUE, message=FALSE, warning=FALSE}
library(dplyr)
library(prettyglm)
data('titanic')

# Easy way to convert multiple columns to a factor.
columns_to_factor <- c('Pclass',
                       'Sex',
                       'Cabin', 
                       'Embarked',
                       'Cabintype')
meanage <- base::mean(titanic$Age, na.rm=T)
titanic  <- titanic  %>%
  dplyr::mutate_at(columns_to_factor, list(~factor(.))) %>%
  dplyr::mutate(Age =base::ifelse(is.na(Age)==T,meanage,Age)) %>% 
  dplyr::mutate(Age_Cat = Hmisc::cut2(Age, levels.mean = TRUE, g =10))

# Build a basic glm
survival_model <- stats::glm(Survived ~ Pclass + 
                                        Sex + 
                                        Fare +
                                        Age_Cat +
                                        Embarked + 
                                        SibSp + 
                                        Parch, 
                             data = titanic, 
                             family = binomial(link = 'logit'))
```

## Plot coefficients {.tabset}

A model relativity is a transform of the model estimate. By default `pretty_relativities()` uses 'exp(estimate)-1' which is useful for GLM's which use a log or logit link function. 

The term 'relativity' is some times referred to as "odds-ratio" or "Likelihood". You can customize the label with the `relativity_label` input.

### Categorical Variables

For categorical variables `pretty_relativities()` creates an interactive duel axis plot, which plots the fitted relativity on one y axis, and the number of records in that category on the other y axis. 

```{r visualise rels, echo=TRUE, message=FALSE, warning=FALSE}
pretty_relativities(feature_to_plot= 'Embarked',
                    model_object = survival_model,
                    relativity_label = 'Liklihood of Survival'
                    )
```

### Categorical Variables With Numeric Axis

If you want to plot a categorical variable on a numeric axis. You can set `plot_factor_as_numeric` equal to TRUE.

```{r visualise rels num, echo=TRUE, message=FALSE, warning=FALSE}
pretty_relativities(feature_to_plot= 'Age_Cat',
                    model_object = survival_model,
                    relativity_label = 'Liklihood of Survival',
                    plot_factor_as_numeric = T
                    )
```


### Continuous Variables

For continuous variables `pretty_relativities()` will plot the relativity over the variables range, and the density of that variable on a duel axis.

If desired you can cut off the tail end of the distributions with `upper_percentile_to_cut` or `lower_percentile_to_cut`. 

```{r visualise rels 2, echo=TRUE}
pretty_relativities(feature_to_plot= 'Fare',
                    model_object = survival_model,
                    relativity_label = 'Liklihood of Survival',
                    upper_percentile_to_cut = 0.1)
```
