---
title: 'creating spline relativity plots'
author:
- name: Jared Fowler
output:
  html_document: 
    number_sections: no
vignette: >
  %\VignetteIndexEntry{prettyglm: Beautiful Visualisations for Generalized Linear Models}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

To highlight some more of `prettyglm`'s functionality we will now build a logistic regression model with a spline.

## Pre-processing

A critical step for this package to work is to **set all categorical predictors as factors**. Before we fit a spline we will fit the age variable as a categorical variable to understand the trend.

```{r preprocessing 1, echo=TRUE, message=FALSE, warning=FALSE}
library(dplyr)
library(prettyglm)
data('titanic')

# Easy way to convert multiple columns to a factor.
columns_to_factor <- c('Pclass',
                       'Sex',
                       'Cabin', 
                       'Embarked',
                       'Cabintype')
meanage <- base::mean(titanic$Age, na.rm=T)
titanic  <- titanic  %>%
  dplyr::mutate_at(columns_to_factor, list(~factor(.))) %>%
  dplyr::mutate(Age = base::ifelse(is.na(Age)==T,meanage,Age)) %>% 
  dplyr::mutate(Age_Cat = Hmisc::cut2(Age, levels.mean = TRUE, g =10)) %>% 
  dplyr::mutate(Fare_Cat = Hmisc::cut2(Fare, levels.mean = TRUE, g =10))

# Build a basic glm
survival_model <- stats::glm(Survived ~ Pclass + 
                                        Sex + 
                                        Sex:Fare_Cat +
                                        Age_Cat +
                                        Embarked + 
                                        SibSp + 
                                        Parch, 
                             data = titanic, 
                             family = binomial(link = 'logit'))
```

## Understanding the trend {.tabset}

By setting `plot_factor_as_numeric` equal to TRUE in `pretty_relativities()` we can plot understand the bucketed categorical predictors trend. Setting `plot_factor_as_numeric` equal to TRUE also works for interactions like Sex:Fare.

### Age

We will fit a knot point at 18 and 35.

```{r fiting age trend}
pretty_relativities(feature_to_plot= 'Age_Cat',
                    model_object = survival_model,
                    relativity_label = 'Liklihood of Survival',
                    plot_factor_as_numeric = T
                    )
```

### Fare

We will fit a knot point at 55.

```{r fiting fare trend}
pretty_relativities(feature_to_plot= 'Sex:Fare_Cat',
                    model_object = survival_model,
                    relativity_label = 'Liklihood of Survival',
                    plot_factor_as_numeric = T,
                    iteractionplottype = 'colour',
                    facetorcolourby = 'Sex')
```

## Creating the spline

`prettyglm` includes some useful functions to assist in building splines. `splineit()` takes the minimum and maximum points of a spline to create the splined column. An example workflow using `dplyr` is shown below.

```{r creating spline plints}
titanic  <- titanic  %>%
  dplyr::mutate(Age_0_18 = prettyglm::splineit(Age,0,18),
                Age_18_35 = prettyglm::splineit(Age,18,35),
                Age_35_120 = prettyglm::splineit(Age,35,120)) %>%
  dplyr::mutate(Fare_0_55 = prettyglm::splineit(Fare,0,55),
                Fare_55_600 = prettyglm::splineit(Fare,55,600))

survival_model4 <- stats::glm(Survived ~ Pclass +
                                         Sex:Fare_0_55 +
                                         Sex:Fare_55_600 +
                                         Age_0_18 +
                                         Age_18_35 +
                                         Age_35_120 +
                                         Embarked +
                                         SibSp +
                                         Parch,
                              data = titanic,
                              family = binomial(link = 'logit'))
```

## Visualising the spline

### Creating a table of model coefficients

For interactions variables are grouped on the left pane under `Variables`. It is important to provide the correct `spline_seperator`

```{r visualise coefficients type spline, echo=TRUE}
pretty_coefficients(survival_model4, 
                    significance_level = 0.1,
                    spline_seperator = '_')
```

### Create plots of fitted coefficients using pretty_relativities

#### Single Variable Splines

You also need to provide a `spline_seperator` input in `pretty_relativities()`. 

```{r visualise age spine, echo=TRUE, message=FALSE, warning=FALSE}
pretty_relativities(feature_to_plot= 'Age',
                    model_object = survival_model4,
                    relativity_label = 'Liklihood of Survival',
                    spline_seperator = '_'
                    )
```

#### Interacted Splines {.tabset}

##### Colour

By default `pretty_relativities()` will colour by the factor variable.

```{r visualise fare spine, echo=TRUE, message=FALSE, warning=FALSE}
pretty_relativities(feature_to_plot= 'Sex:Fare',
                    model_object = survival_model4,
                    relativity_label = 'Liklihood of Survival',
                    spline_seperator = '_',
                    upper_percentile_to_cut = 0.03
                    )
```

##### Facet

If you prefer to facet by the factor variable, change `iteractionplottype` to "facet" 

```{r visualise fare Facet, echo=TRUE, message=FALSE, warning=FALSE}
pretty_relativities(feature_to_plot= 'Sex:Fare',
                    model_object = survival_model4,
                    relativity_label = 'Liklihood of Survival',
                    spline_seperator = '_',
                    upper_percentile_to_cut = 0.03,
                    iteractionplottype = 'facet'
                    )
```
