---
title: "prettyglm-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{prettyglm-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r include=FALSE}
# knitr::opts_chunk$set(
#   collapse = TRUE,
#   comment = "#>"
# )
```

# Introduction to prettyglm

When working with Generalized Linear Models it is often useful to create informative and beautiful summaries of the fitted model coefficients.This document introduces prettyglms’s main sets of functions, and shows you how to apply them.

```{r setup, include=FALSE}
library(dplyr)
library(prettyglm)
#library(tidymodels)
```

## Data: titanic

To explore the functionality of prettyglm we will use the titanic data set to perform logistic regression. This data set was sourced from https://www.kaggle.com/c/titanic/data and contains information about passengers aboard the titanic, and a target variable which indicates if they survived. 

```{r load data, echo=TRUE}
data('titanic')
head(titanic) %>%
  knitr::kable(table.attr = "style='width:30%;'" ) %>% 
  kableExtra::kable_classic(full_width = T, position = "center")
```

## Pre-processing

A critical step for this package to work well is to **set all categorical predictors as factors**.

```{r preprocessing, echo=TRUE}
# Easiest way to convert multiple columns to a factor.
columns_to_factor <- c('Pclass',
                       'Sex',
                       'Cabin', 
                       'Embarked',
                       'Cabintype')
titanic  <- titanic  %>%
  dplyr::mutate_at(columns_to_factor, list(~factor(.)))
```


## Building a glm

For this vignette we will use `stats::glm()` but `prettyglm`  also supports `parsnip` and `workflow` model objects which use the `glm` model engine.

```{r build model, echo=TRUE}
survival_model <- stats::glm(Survived ~ Pclass + Sex + Age + Fare + Embarked + SibSp + Parch + Cabintype, 
                             data = titanic, 
                             family = binomial(link = 'logit'))
```


## Create pretty table of model coefficients with `pretty_coefficients()`

`pretty_coefficients()` allows you to create a pretty table of model coefficients, including categorical base levels.

```{r visualise coefficients, echo=TRUE}
pretty_coefficients(survival_model)
```

You can also complete a type III test on the coefficients by specifying a `type_iii` argument.

```{r visualise coefficients type iii, echo=TRUE}
pretty_coefficients(survival_model, type_iii = 'Wald')
```

or return a data frame by setting `return_data` to `TRUE`.


## Create beautiful plots of variable relativities with `pretty_relativities()`

`pretty_relativities()` creates an interactive duel axis plot (via plotly), which plots the fitted relativity and the number of records in that category.


```{r visualise rels, echo=TRUE}
pretty_relativities(feature_to_plot= 'Embarked',
                    model_object = survival_model)
```




<!-- ## Building a tidymodel -->

<!-- ### parsnip model object -->

<!-- ```{r build tidymodel} -->
<!-- # parsnip model -->
<!-- pasnip_model <- linear_reg() %>% -->
<!--   set_engine("lm") %>% -->
<!--   fit(Survived ~ Pclass + Sex + Age + Fare + Embarked + SibSp + Parch + Cabintype, data = titanic) -->
<!-- ``` -->


<!-- ### workflow model  -->

<!-- ```{r workflow} -->
<!-- # workflow object -->
<!-- titanic$Survived <- as.factor(titanic$Survived) -->
<!-- model_recipe <- recipe(Survived ~ Pclass + Sex + Age + Fare + Embarked + SibSp + Parch + Cabintype, data = titanic) -->

<!-- Model_type <- logistic_reg()  %>% -->
<!--   set_engine("glm") %>% -->
<!--   set_mode("classification") -->

<!-- tidy_workflow <- workflow() %>% -->
<!--   add_recipe(model_recipe) %>% -->
<!--   add_model(Model_type) %>% -->
<!--   fit(titanic) -->
<!-- ``` -->



