---
title: "Pretty Coefficients: Beautiful Model Output"
description: "Learn how to create publication-ready coefficient tables from your GLM models"
author: "Jared Fowler"
date: today
format:
  html:
    theme: cosmo
    toc: true
    toc-depth: 2
    code-fold: false
    code-summary: "Show code"
    highlight-style: github
    embed-resources: true
---

## Introduction

The `pretty_coefficients()` function transforms model coefficients into publication-ready tables with variable importance scores, transformations, and interactive features.

```{r}
#| message: false
#| warning: false
devtools::load_all()
library(prettyglm)
library(dplyr)
```

## Basic Usage

Load the example data and fit a simple model:

```{r}
data('titanic')

# Prepare the data
columns_to_factor <- c(
  'Pclass',
  'Sex',
  'Cabin',
  'Embarked',
  'Cabintype',
  'Survived'
)
meanage <- mean(titanic$Age, na.rm = TRUE)

titanic <- titanic |>
  mutate(across(all_of(columns_to_factor), factor)) |>
  mutate(Age = ifelse(is.na(Age), meanage, Age))
```


# EDA

```{r}
one_way_ave(
  feature_to_plot = 'Age',
  target_variable = 'Survived',
  data_set = titanic,
  plot_type = 'actuals'
)

one_way_ave(
  feature_to_plot = 'Age',
  target_variable = 'Survived',
  data_set = titanic,
  plot_type = 'actuals',
  facetby = 'Sex'
)

one_way_ave(
  feature_to_plot = 'Pclass',
  target_variable = 'Survived',
  data_set = titanic,
  plot_type = 'actuals',
  facetby = 'Cabintype' #,
  # facet_direction = 'horizontal'
)

one_way_ave(
  feature_to_plot = 'Age',
  target_variable = 'Survived',
  data_set = titanic,
  plot_type = 'actuals',
  facetby = 'Cabintype',
  facet_direction = 'horizontal'
)
```

Fit a logistic regression model:

```{r}
survival_model <- glm(
  Survived ~ Pclass + Sex + Age + Fare + Embarked + SibSp + Parch + Cabintype,
  data = titanic,
  family = binomial(link = 'logit')
)
```

Display pretty coefficients:

```{r}
pretty_coefficients(survival_model, type_iii = 'Wald')
```

## Advanced Features

### Spline Transformations

Create spline features for continuous variables:

```{r}
titanic <- titanic |>
  mutate(
    Age_0_25 = splineit(Age, 0, 25),
    Age_25_50 = splineit(Age, 25, 50),
    Age_50_120 = splineit(Age, 50, 120),
    Fare_0_250 = splineit(Fare, 0, 250),
    Fare_250_600 = splineit(Fare, 250, 600)
  )
```

Fit a model with splines and interactions:

```{r}
survival_model_spline <- glm(
  Survived ~ Pclass +
    Age_0_25 +
    Age_25_50 +
    Age_50_120 +
    Sex:Fare_0_250 +
    Sex:Fare_250_600 +
    Embarked +
    SibSp +
    Parch +
    Cabintype,
  data = titanic,
  family = binomial(link = 'logit')
)
```

### Custom Transformations and Variable Importance

Display coefficients with odds ratios and permutation importance:

```{r}
pretty_coefficients(
  survival_model_spline,
  relativity_transform = 'exp(estimate)-1',
  spline_seperator = '_',
  vimethod = 'permute',
  target = 'Survived',
  metric = "roc_auc",
  event_level = 'second',
  pred_wrapper = predict.glm,
  smaller_is_better = FALSE,
  train = survival_model_spline$data,
  reference_class = 0
)
```

## Key Parameters

- **`relativity_transform`**: Transform coefficients (e.g., `'exp(estimate)-1'` for odds ratios)
- **`vimethod`**: Variable importance method (`'permute'`, `'shap'`, etc.)
- **`target`**: Target variable for importance calculation
- **`metric`**: Performance metric for importance (`'roc_auc'`, `'rmse'`, etc.)
- **`train`**: Training data for variable importance computation
- **`reference_class`**: Reference class for classification models

## Next Steps

Explore more advanced features in the package documentation and experiment with different models and transformations.
